analysis

### 2019-12-05 03_Preliminary_analysis.Rmd
Correcting/updating broken code

### Fungicides
#### Fungicide type
The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).  
All data explored below are a list of mean values from each treatment applied in each experiment. Some experiments have in-season observations of disease incidence and severity, however here we have summarised the data to show only the end of season observations.    
```{r Fungicides}
PM_MB_means %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   theme_usq() +
   coord_flip()
```

   - Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment.

@@

   - Perhaps best way forward is to do an analysis of only the triazoles/demethylation inhibitors. Then do another including azoxystrobin as a comparison.

@@

```{r Fungicide_x_nSprays, message=FALSE}
PM_MB_means %>%
   group_by(fungicide, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

class(PM_MB_means$fungicide)

PM_MB_means %>%
   mutate(fungicide = as.factor(PM_MB_means$fungicide)) %>%
   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide != "pyrazophos" &
         fungicide != "control" &
         fungicide != "benomyl" &
         fungicide != "Acibenzolar-S-methyl"
   ) %>%
   mutate(fungicide = factor(fungicide, 
                             levels = c("carbendazim", "pyraclostrobin",
                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
                                        "tebuconazole", "propiconazole", 
                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
   ggplot(aes(y = prop_YG, x = fungicide)) +
   facet_grid(rows = vars(total_fungicide)) +
   geom_boxplot(aes(fill = fungicide, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
   theme_usq() +
   theme(legend.position = "none") +
   # coord_cartesian() +
   # scale_x_discrete(
   #    limits = c(
   #       "200 g/l  Tebuconazole + 120 g/l  Azoxystrobin",
   #       "Propiconazole",
   #       "Tebeconazole",
   #       "200g/L Azoxystrobin + 80 g/L Cyproconazole",
   #       "Sulphur",
   #       "Carbendazim",
   #       "Pyraclostrobin",
   #       "Azoxystrobin"
   #    )
   # ) +
   #  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3))+
   coord_flip()
#scale_x_continuous(limits = c(-0.3,0.6))

>>>>

The data plotted below are from `r length(unique(PM_MB_means$trial_ref))` field trials between (`r first(levels(PM_MB_means$year))` - `r last(levels(PM_MB_means$year))`) of which the details are described in [Studies considered in meta-analysis section](#studies-considered-in-meta-analysis).  
All data explored below are a list of mean values from each treatment applied in each experiment. Some experiments have in-season observations of disease incidence and severity, however here we have summarised the data to show only the end of season observations.

### Fungicides
#### Fungicide type
Let's explore how many different types of fungicide were used and at what frequency.

```{r Fungicides}
PM_MB_means %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   theme_usq() +
   coord_flip()
```

   - Tebuconazole and propiconazole could be pooled as a triazole or demethylation inhibitors (DMI) fungicide treatment.

@@

   - Perhaps best way forward is to do an analysis of only the triazoles/DMIs. Then do another including azoxystrobin as a comparison.

@@

```{r Fungicide_x_nSprays_tble, message=FALSE}
PM_MB_means %>%
   group_by(fungicide, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

Plot one and two applications of the main sprays

```{r Fungicide_x_nSprays_tble, message=FALSE}

PM_MB_means[PM_MB_means$fungicide_ai == "sulphur (SC)"|
               PM_MB_means$fungicide_ai == "sulphur (WP)"|
               PM_MB_means$fungicide_ai == "sulphur (Ultra SC)","fungicide_ai"] <- "sulphur"

PM_MB_means$sprays <- sapply(PM_MB_means$total_fungicide, FUN = function(x){if(x == 1){return("one")}else{return("plus")}})

PM_MB_means %>%
   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide_ai != "pyrazophos" &
         fungicide_ai != "control" &
         fungicide_ai != "benomyl" &
         fungicide_ai != "Acibenzolar-S-methyl") %>%
   mutate(fungicide_ai = factor(fungicide_ai, 
                             levels = c("carbendazim", "pyraclostrobin",
                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
                                        "tebuconazole", "propiconazole", 
                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   facet_grid(rows = vars(total_fungicide)) +
   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
   theme_usq() +
   theme(legend.position = "none") +
   coord_flip()

PM_MB_means %>%
   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
#   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide_ai != "pyrazophos" &
         fungicide_ai != "control" &
         fungicide_ai != "benomyl" &
         fungicide_ai != "Acibenzolar-S-methyl") %>%
   mutate(fungicide_ai = factor(fungicide_ai, 
                             levels = c("carbendazim", "pyraclostrobin",
                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
                                        "tebuconazole", "propiconazole", 
                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   facet_grid(rows = vars(sprays)) +
   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
   theme_usq() +
   theme(legend.position = "none") +
   coord_flip()
